Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-29 pirouette_supplement.tex
Use 'TESS' in the bibliography (that is, only the package)
Cite Houhna's paper again
Add note in supmat what is needed in a thesis to have the refs refer properly
Add LaTeX comments to ensure a correct thesis
Changes @rsetienne

\verb;pirouette; is free, libre and open source software available at 
\begin{sloppypar}
  \url{http://github.com/richelbilderbeek/pirouette},
\end{sloppypar}
licensed under the GNU General Public License version 3.
\verb;pirouette; depends on multiple packages, which are:
\verb;ape; [\cite{ape}],
\verb;assertive; [\cite{assertive}],
\verb;babette; [\cite{bilderbeek2018babette}],
\verb;DDD; [\cite{DDD}],
\verb;devtools; [\cite{devtools}],
\verb;dplyr; [\cite{dplyr}],
\verb;ggplot2; [\cite{ggplot2}],
\verb;knitr; [\cite{knitr}],
\verb;lintr; [\cite{lintr}],
\verb;magrittr; [\cite{magrittr}],
\verb;mcbette; [\cite{mcbette}],
\verb;nLTT; [\cite{nLTT}],
\verb;phangorn; [\cite{phangorn}],
\verb;phytools; [\cite{phytools}],
\verb;plyr; [\cite{plyr}],
\verb;rappdirs; [\cite{rappdirs}],
\verb;rmarkdown; [\cite{rmarkdown}],
\verb;Rmpfr; [\cite{Rmpfr}],
\verb;stringr; [\cite{stringr}],
\verb;TESS; [\cite{TESS}],
\verb;testit; [\cite{testit}], 
\verb;testthat; [\cite{testthat}] and
\verb;tidyr; [\cite{tidyr}].

@@

It is then possible to use the likelihood function 
$L_{\mathit{T}}$ for this diversification model to find 
the parameters $\theta^{*}_{\mathit{T}}$ 
(e.g. speciation and extinction rates, in case of a BD model) 
that maximize this likelihood applied to the true tree, conditioned on its number of tips $n_{\mathit{G}}$:
\begin{align}
    \max[L_{\mathit{T}}(\theta_{\mathit{T}}|\tau_{\mathit{G}}, n_{\mathit{G}})] 
\rightarrow \theta^{*}_{\mathit{T}}.
\end{align}
We use $\theta^{*}_{\mathit{T}}$ to simulate a number 
$n_{\mathit{T}} = n_{\mathit{G}}$ 
of branching times $\Vec{t}_{\mathit{T}}$ for the twin tree 
$\tau_{\mathit{T}}$, under the process $p_{T}$, 
while preserving the topology. 
We simulate the new branching times using the TESS 
package [\cite{TESS, hohna2016tess}].
\new{
  For simplicity, when simulating phylogenies we assumed a sampling fraction 
  of $100\%$. A different choice might have an effect on model performance.
}

@@

The ESSes of the 'true' pipeline for the best candidate model
are shown in Table \ref{tab:esses_best}. 
From the names of the estimated parameters, it is clear that
the best candidate model has had a TN nucleotide substitution 
model (due to 'kappa1', 'kappa2', 'freqParameter.1', 
'freqParameter.2', 'freqParameter.3', 'freqParameter.4')
a strict clock (no parameter needed to be estimated) and a BD 
model ('BirthDeath', 'BDBirthRate' and 'BDDeathRate').

>>>>

\verb;pirouette; is free, libre and open source software available at 
\begin{sloppypar}
  \url{http://github.com/richelbilderbeek/pirouette},
\end{sloppypar}
licensed under the GNU General Public License version 3.
\verb;pirouette; depends on multiple packages, which are:
\verb;ape; [\cite{ape}],
\verb;assertive; [\cite{assertive}],
\verb;babette; [\cite{bilderbeek2018babette}],
\verb;DDD; [\cite{DDD}],
\verb;devtools; [\cite{devtools}],
\verb;dplyr; [\cite{dplyr}],
\verb;ggplot2; [\cite{ggplot2}],
\verb;knitr; [\cite{knitr}],
\verb;lintr; [\cite{lintr}],
\verb;magrittr; [\cite{magrittr}],
\verb;mcbette; [\cite{mcbette}],
\verb;nLTT; [\cite{nLTT}],
\verb;phangorn; [\cite{phangorn}],
\verb;phytools; [\cite{phytools}],
\verb;plyr; [\cite{plyr}],
\verb;rappdirs; [\cite{rappdirs}],
\verb;rmarkdown; [\cite{rmarkdown}],
\verb;Rmpfr; [\cite{Rmpfr}],
\verb;stringr; [\cite{stringr}],
\verb;TESS; [\cite{TESS,hohna2016tess}],
\verb;testit; [\cite{testit}], 
\verb;testthat; [\cite{testthat}] and
\verb;tidyr; [\cite{tidyr}].

@@

It is then possible to use the likelihood function 
$L_{\mathit{T}}$ for this diversification model to find 
the parameters $\theta^{*}_{\mathit{T}}$ 
(e.g. speciation and extinction rates, in case of a BD model) 
that maximize this likelihood applied to the true tree, conditioned on its number of tips $n_{\mathit{G}}$:
\begin{align}
    \max[L_{\mathit{T}}(\theta_{\mathit{T}}|\tau_{\mathit{G}}, n_{\mathit{G}})] 
\rightarrow \theta^{*}_{\mathit{T}}.
\end{align}
We use $\theta^{*}_{\mathit{T}}$ to simulate a number 
$n_{\mathit{T}} = n_{\mathit{G}}$ 
of branching times $\Vec{t}_{\mathit{T}}$ for the twin tree 
$\tau_{\mathit{T}}$, under the process $p_{T}$, 
while preserving the topology. 
We simulate the new branching times using the TESS 
package [\cite{TESS}].
\new{
  For simplicity, when simulating phylogenies we assumed a sampling fraction 
  of $100\%$. A different choice might have an effect on model performance.
}

@@

The ESSes of the 'true' pipeline for the best candidate model
are shown in Table \ref{tab:esses_best}. 
From the names of the estimated parameters, it is clear that
the best candidate model has had a TN nucleotide substitution 
model (which can be inferred from the parameters'kappa1', 'kappa2', 'freqParameter.1', 
'freqParameter.2', 'freqParameter.3', 'freqParameter.4')
a strict clock (no parameter needed to be estimated) and a BD 
model ('BirthDeath', 'BDBirthRate' and 'BDDeathRate').
